---
title: "CEMACS Experiment Daily Report"
author: "Yusri Yusup, PhD"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Air-sea flux exchanges and weather
Date: `r Sys.Date()`

This page shows the previous day half-hourly 24-hour measurements of carbon dioxide flux, latent and sensible heat fluxes and other weather parameters from the CEMACS eddy covariance station. Data is from the previous day.
Coordinates: (5.49 N, 100.2025 E)


```{r , echo = FALSE, include = FALSE}
source('data_import_web.R') # Using a modified version of data_import.R
require(openair) # To plot wind rose
```


## CO~2~ flux
This plots shows the vertical movement or fluxes of carbon dioxide (CO~2~) from the water and land surfaces surrounding the station.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$co2_flux, pch = 19, xlab = '',
     ylab = '', col = 'orange', ylim = c(-0.5,0.5))
points(df_web$time_stamp[which(df_web$qc_co2_flux == '2')], 
       df_web$co2_flux[which(df_web$qc_co2_flux == '2')], pch = 19, col = 'red')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('CO'['2'],' flux (', mu,'g m'^'-2', ' s'^'-1',')')), 
      line = 2)
```

## CO~2~ footprint
Location of sources CO~2~ flux (90% contribution) using footprint analysis. Note that 'wind_strict_check' is off so sources could be from non-oceanic sources. Values in legend is in ug m[-2] s[-1].

```{r , echo=FALSE, warning=FALSE, message=FALSE}
require(plotrix)
require(colorspace)
require(marmap)
# Usable CO2 index
# Another index for co2 for -5 < co2 < 5
indexCO2_5 <- (df_web$qc_co2_flux==1 | df_web$qc_co2_flux == 0) & df_web$co2_flux > -5 & df_web$co2_flux < 5
# Data management
x_90_polar <- df_web$x_90.[indexCO2_5]/1000
indexNA <- which(is.na(x_90_polar))
# Direction in degrees
wd_polar <- df_web$wind_dir[indexCO2_5]
wd_polar[indexNA] <- NA
# co2 flux
co2_polar <- df_web$co2_flux[indexCO2_5]
co2_polar[indexNA] <- NA
# Remove NA's
x_90_polar <- na.omit(x_90_polar)
wd_polar <- na.omit(wd_polar)
wd_polar_rad <- wd_polar * 2 * pi /360
co2_polar <- na.omit(co2_polar)

# Color code the points
ii <- cut(co2_polar, breaks = seq(min(co2_polar), max(co2_polar), 
                                  by = round((max(co2_polar) - min(co2_polar))/5,2)))
ii <- na.omit(ii)
colorfunc <- colorRampPalette(c("yellow", "green"), alpha = 0.8)(length(ii))



# Change polar to long lat coordinates
x <- ((x_90_polar*1000/110815) * sin(wd_polar_rad)) + 100.2025
y <- ((x_90_polar*1000/110584) * cos(wd_polar_rad)) + 5.49

# Color palette
blues <- c("lightsteelblue4", "lightsteelblue3", "lightsteelblue2", "lightsteelblue1")

# Download bathymetry? might take a few seconds
#bath_ppinang <- getNOAA.bathy(lon1 = 99, lon2 = 105, lat1 = 1, lat2 = 6, resolution = 1)
load(file='/home/eddy_cov/Documents/muka_head/bath_ppinang.RData')

# plot the bathymetry
layout(matrix(1:2, ncol = 2), width = c(2,1), height = c(1,1))

plot(bath_ppinang, image = TRUE, land = TRUE, lwd = 0.1, 
     xlim = c(100.20, 100.25), ylim = c(5.42, 5.62), 
     cex.lab = 1, cex.axis = 0.8,
     bpal = list(c(0, max(bath_ppinang), 'grey'), c(min(bath_ppinang), 0, blues)),
     xlab = '', ylab = '')
mtext(side = 1, 'Longitude', line = 2)
mtext(side = 2, 'Latitude', line = 2)
points(100.2025, 5.4750, pch = 19, col = 'black', cex = 1)
scaleBathy(bath_ppinang, deg = 0.045, x = 'bottomright', inset = 5, cex = 0.8)
points(x, y, pch = 19, col = colorfunc, cex = 2)

legend_image <- grDevices::as.raster(matrix(colorfunc, ncol = 1))
plot(c(0,2),c(min(co2_polar), max(co2_polar)), 
     type = 'n', axes = FALSE, xlab = '', ylab = '', main = 'Flux')
text(x = 1, y = seq(min(co2_polar), max(co2_polar), l = 3),
     labels = c(round(min(co2_polar),3), 
                round(median(co2_polar),3), 
                round(max(co2_polar), 3)))
rasterImage(legend_image, 0, min(co2_polar), 0.4, max(co2_polar))


```

## Latent heat (LE)
This plots shows the vertical movement of moisture or latent heat (LE) from the water and land surfaces surrounding the station.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$LE, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'blue')
points(df_web$time_stamp[which(df_web$qc_LE == '2')], 
       df_web$LE[which(df_web$qc_LE == '2')], pch = 19, col = 'red')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('LE ', '(W m'^'-2',')')), 
      line = 2)
```


## Sensible heat (H)
This plots shows the vertical movement or fluxes of dry heat or sensible heat (H) from the water and land surfaces surrounding the station.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$H, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'red')
points(df_web$time_stamp[which(df_web$qc_H == '2')], 
       df_web$H[which(df_web$qc_H == '2')], pch = 19, col = 'blue')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('H ', '(W m'^'-2',')')), 
      line = 2)
```

## Global and net radiation 
Global radiation (RG) is red and net radiation (RN) is orange.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$RG_1_1_1, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'red',ylim=c(-200,1000))
lines(df_web$time_stamp, df_web$RN_1_1_1, type = 'o', pch = 19, col = 'orange')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('RG and RN ', '(W m'^'-2',')')), 
      line = 2)
```

## Wind Speed (WS)
Wind speed for 24 hours.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$wind_speed, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'black')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('WS ', '(m ', 's'^'-1',')')), 
      line = 2)
```

## Wind Direction (WD)
Wind direction for 24 hours. Zero degrees is North and, moving clockwise, 90 degrees is east.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$wind_dir, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'black')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('WD ', '(', degree, ')')), 
      line = 2)
```

## Wind rose
Wind rose for 24 hours. Zero degrees is North and, moving clockwise, 90 degrees is east.

```{r , echo=FALSE, warning=FALSE, message=FALSE}
windRose(df_web, ws = 'wind_speed', wd = 'wind_dir', paddle = FALSE)

```

## Atmospheric temperature (T)
Atmospheric temperature for 24 hours.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$TA_1_1_1, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'black')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('T (', degree,'C)')), 
      line = 2)
```

## Relative Humidity (RH)
Relative humidity for 24 hours.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$RH_1_1_1, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'black')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('RH (%)')), 
      line = 2)
```

## Underwater temperature (T)
Underwater temperature (T) in degree celsius near the surface of the water (dark blue). The temperature at the surface would dip to cool temperatures due to low tide which causes the sensor to be above the water surface.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$TS_1_1_1, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'darkblue')
#lines(df_web$time_stamp, df_web$TS_2_1_1, col = 'lightblue',type ='o', pch =19)
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('T (', degree,'C)')), 
      line = 2)
```


## Rain
The 30-min accumulative rain or precipitation (Precip) in mm.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$precip_1_1_1, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'darkblue')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('30-min Cumulative Rain (mm)')), 
      line = 2)
```