---
title: "CEMACS Experiment Daily Report"
author: "Yusri Yusup, PhD"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Air-sea flux exchanges and weather
Date: `r Sys.Date()`

This page shows the previous day half-hourly 24-hour measurements of carbon dioxide flux, latent and sensible heat fluxes and other weather parameters from the CEMACS eddy covariance station. Data is from 18:00 to 17:30, the following day.


```{r , echo = FALSE, include = FALSE}
source('data_import_web.R') # Using a modified version of data_import.R
require(openair) # To plot wind rose
```


## CO~2~ flux
This plots shows the vertical movement or fluxes of carbon dioxide (CO~2~) from the water and land surfaces surrounding the station.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$co2_flux, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'orange', ylim = c(-0.5,0.5))
points(df_web$time_stamp[which(df_web$qc_co2_flux == '2')], 
       df_web$co2_flux[which(df_web$qc_co2_flux == '2')], pch = 19, col = 'red')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('CO'['2'],' flux (', mu,'g m'^'-2', ' s'^'-1',')')), 
      line = 2)
```


## Latent heat (LE)
This plots shows the vertical movement of moisture or latent heat (LE) from the water and land surfaces surrounding the station.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$LE, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'blue')
points(df_web$time_stamp[which(df_web$qc_LE == '2')], 
       df_web$LE[which(df_web$qc_LE == '2')], pch = 19, col = 'red')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('LE ', '(W m'^'-2',')')), 
      line = 2)
```


## Sensible heat (H)
This plots shows the vertical movement or fluxes of dry heat or sensible heat (H) from the water and land surfaces surrounding the station.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$H, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'red')
points(df_web$time_stamp[which(df_web$qc_H == '2')], 
       df_web$H[which(df_web$qc_H == '2')], pch = 19, col = 'blue')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('H ', '(W m'^'-2',')')), 
      line = 2)
```

## Global and net radiation 
Global radiation (RG) is red and net radiation (RN) is orange.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$RG_1_1_1, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'red',ylim=c(-200,1000))
lines(df_web$time_stamp, df_web$RN_1_1_1, type = 'o', pch = 19, col = 'orange')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('RG and RN ', '(W m'^'-2',')')), 
      line = 2)
```

## Wind Speed (WS)
Wind speed for 24 hours.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$wind_speed, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'black')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('WS ', '(m ', 's'^'-1',')')), 
      line = 2)
```

## Wind Direction (WD)
Wind direction for 24 hours. Zero degrees is North and, moving clockwise, 90 degrees is east.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$wind_dir, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'black')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('WD ', '(', degree, ')')), 
      line = 2)
```

## Wind rose
Wind rose for 24 hours. Zero degrees is North and, moving clockwise, 90 degrees is east.

```{r , echo=FALSE, warning=FALSE, message=FALSE}
windRose(df_web, ws = 'wind_speed', wd = 'wind_dir', paddle = FALSE)

```

## Atmospheric temperature (T)
Atmospheric temperature for 24 hours.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$TA_1_1_1, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'black')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('T (', degree,'C)')), 
      line = 2)
```

## Relative Humidity (RH)
Relative humidity for 24 hours.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$RH_1_1_1, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'black')
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('RH (%)')), 
      line = 2)
```

## Underwater temperature (T)
Underwater temperature (T) in degree celsius near the surface of the water (dark blue). The temperature at the surface would dip to cool temperatures due to low tide which causes the sensor to be above the water surface.

```{r , echo=FALSE, warning = FALSE, message = FALSE}
plot(df_web$time_stamp, df_web$TS_1_1_1, type ='o', pch = 19, xlab = '',
     ylab = '', col = 'darkblue')
#lines(df_web$time_stamp, df_web$TS_2_1_1, col = 'lightblue',type ='o', pch =19)
mtext(side = 1, 'Time', line = 2)
mtext(side = 2, expression(paste('T (', degree,'C)')), 
      line = 2)
```
